Arc Blanc: a real time ocean simulation framework

### 2025-01-10 paper.tex
Clarify fig 11

The functions $f(x)$ and $g(z)$ are then used to obtain the height of the mask as follows,
but using the user factor $b_w$ to allow more user control:
\begin{equation}
	h(\mathbf x)=b_w\left(f(x)+g(z)\right).
\end{equation}

@@

Figure \ref{fig:mask} shows some views of the application of this interactive waves process for a simple rectangular boat.

@@

	\subfloat[A theoretical view of the water height function $h(\mathbf x,t)$ that will be applied to a simple rectangle.]
	{
		\includegraphics[width=0.25\textwidth]{Figures/Mask3D_theoric_view.png}
		\label{subfig:maskTheoreticalView}
	}
	\hspace{1cm}
	\subfloat[The mask of a simple boat encoded in a single channel texture.]
	{
		\includegraphics[width=0.25\textwidth]{Figures/MaskHeightMap.png}
		\label{subfig:maskHeightMap}
	}
	\hspace{1cm}
	\subfloat[The mask of a simple boat in a 3D scene with a very low sea state.]
	{
		\includegraphics[width=0.25\textwidth]{Figures/Mask3D-contrast.png}
		\label{subfig:mask3D}
	}
	\caption{Three different views of the mask.}
	\label{fig:mask}
\end{figure}

>>>>

The functions $f(x)$ and $g(z)$ are then used to obtain the height of the mask as follows,
but using the user factor $b_w$ to allow more user control:
\begin{equation}
	\label{equa:mask_full}
	h(\mathbf x)=b_w\left(f(x)+g(z)\right).
\end{equation}

@@

Figure \ref{fig:mask} shows some views of the application of this interactive waves process.

@@

	\subfloat[A theoretical view of the height of the mask, with input a simple rectangle.]
	{
		\includegraphics[width=0.25\textwidth]{Figures/Mask3D_theoric_view.png}
		\label{subfig:maskTheoreticalView}
	}
	\hspace{1cm}
	\subfloat[The height of the mask of a simple boat encoded in a single channel texture.]
	{
		\includegraphics[width=0.25\textwidth]{Figures/MaskHeightMap.png}
		\label{subfig:maskHeightMap}
	}
	\hspace{1cm}
	\subfloat[The height of the mask of a simple boat in a 3D scene with a very low sea state. Boat rendering and wave propagation has been disabled to only display the initial step of the height of the mask.]
	{
		\includegraphics[width=0.25\textwidth]{Figures/Mask3D-contrast.png}
		\label{subfig:mask3D}
	}
	\caption{Three different views of the height of the mask defined by Equation \ref{equa:mask_full}.}
	\label{fig:mask}
\end{figure}
